### Config files {-}

#### YAML {-}

Below is example code of how to read in and write out yaml files. The same functions, documented and tested, can be found in the [utilsR](https://github.com/holmesjoli/utilsR) package. 

##### Example file {-}

```{r, echo = TRUE, eval = FALSE}
## You can add comments to YAML!
VAR1: 1
VAR2: 2
```

##### Import {-}

```{r, echo = TRUE, eval = FALSE}
library(yaml)

config <- yaml.load_file("./config.yaml")

var1 <- config$VAR1
var2 <- config$VAR2
```

Note: Avoid warnings by adding a final line without any spaces or indents in it!

##### Update {-}

```{r, echo = TRUE, eval = FALSE}
library(yaml)

config$var3 <- "VAR3"
yml <- yaml::as.yaml(config)
write(yml, "./config.yaml")
```

#### JSON {-}

Below is example code of how to read in and write out json files. The same functions, documented and tested, can be found in the [utilsR](https://github.com/holmesjoli/utilsR) package. 

##### Example file {-}

```{r, echo = TRUE, eval = FALSE}
{
"VAR1" = 1,
"VAR2" = 2
}
```

##### Import {-}

```{r, echo = TRUE, eval = FALSE}
library(rjson)

config <- rjson::fromJSON(file = "./config.json")
```

##### Update {-}

```{r, echo = TRUE, eval = FALSE}
library(rjson)
library(jsonlite)

json <- rjson::toJSON(config)
jsonlist::write_json(config, file = "./config.json")
```

#### CSV {-}

##### Example file {-}

```{r, eval = FALSE, echo = TRUE}
|VAR1 | VAR2|
|-----|-----|
|  1  |  2  |
```

##### Import {-}

```{r, echo = TRUE, eval = FALSE}
config <- read.csv("./config.csv")

#OR

library(readr)

config <- read_csv("./config.csv")

var1 <- config$VAR1
var2 <- config$VAR2
```

##### Update {-}

```{r, echo = TRUE, eval = FALSE}
config$var3 <- "VAR3"
write.csv(config, "./config.csv", row.names = FALSE)
```
