# Preface {-}

I started thinking about how to be a better programmer while I worked for Mathematica Policy Research. Mathematica is a mid-size company, with 100s of on-going projects, and at Mathematica every project did it differently. 

However, within the programmer community at Mathematica, there was a strong push, by myself and others, to make best practices more systematic, standardized, to make code efficient, high-quality, and more robust to errors. It is from many of their senior programmers, who invested there time to teach me, that I learned these techniques. It was with these folks, that I started to develop the ideas and methods for this book. A big thanks to Eva Ward, Brian Hunscher, Linus Marco, Michael Sisti, and many others! 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE)
```

# (PART) Robust, Quality Code {-}

```{r child = "Section1/introduction/main.Rmd"}
```

```{r child = "Section1/reproducibility/main.Rmd"}
```

```{r child = "Section1/quality/main.Rmd"}
```

```{r child = "Section1/efficiency/main.Rmd"}
```

# (PART) Languages {-}

```{r, child = "Section2/Python/main.Rmd"}
```

```{r, child = "Section2/R/main.Rmd"}
```

# (PART) Other {-}

```{r child = "Section3/web/main.Rmd"}
```

```{r child = "Section3/data-visualization/main.Rmd"}
```

# (PART) Appendix {-}
```{r child = "Appendix/main.Rmd"}
```