### Config files {-}

#### YAML {-}

Below is example code of how to read in and write out yaml files. The same functions, documented and tested, can be found in the [utilsPy](https://github.com/holmesjoli/utilsPy) package.

##### Example file {-}

```{r, echo = TRUE, eval = FALSE}
## You can add comments to YAML!
VAR1: 1
VAR2: 2
```

##### Install {-}

```{python, eval = FALSE, echo = TRUE}
conda install pyyaml
```

##### Import {-}

```{python, eval = FALSE, echo = TRUE}
import yaml

with open("config.yaml", "r", encoding="utf-8") as cf:
	config = yaml.load(cf)
```

##### Update {-}

```{python, eval = FALSE, echo = TRUE}
import yaml

config["var3"] = "VAR3"

with open('config.yaml', 'w') as fp:
    yaml.dump(config, fp)
```

[Source](https://stackoverflow.com/questions/28557626/how-to-update-yaml-file-using-python)

#### JSON {-}

Below is example code of how to read in and write out json files. The same functions, documented and tested, can be found in the [utilsPy](https://github.com/holmesjoli/utilsPy) package. 

##### Example file {-}

```{r, echo = TRUE, eval = FALSE}
{
"VAR1" = 1,
"VAR2" = 2
}
```

##### Install {-}

```{python, eval = FALSE, echo = TRUE}
conda install json
```

##### Import {-}

```{python, eval = FALSE, echo = TRUE}

import json

with open('config.json') as cf:
	config = json.load(cf)
```

#### CSV {-}

##### Example file {-}

```{r, eval = FALSE, echo = TRUE}
|VAR1 | VAR2|
|-----|-----|
|  1  |  2  |
```

##### Install {-}

```{python, eval = FALSE, echo = TRUE}
conda install pandas
```

##### Import {-}

```{python, eval = FALSE, echo = TRUE}
import pandas as pd

config = pd.read_csv("path_to_csv")
```
